Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
add contributions

\item TODO 1

\item TODO 2

@@

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantization step, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantization step of  ADC and DAC.
% 
\end{myassumption}

@@

In more detail, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
assuming a precision \param{I_b}{F_b} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with a robust algorithm for verifying closed-loop stability to
compute a parametric solution for a digital controller given a continuous
(or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.

>>>>

\item We exploit a CEGIS-based approach, that uses inductive synthesis
in conjunction with a formal verification algorithm, for synthesising 
correct-by-design robust digital controllers for non-fragile closed-loop 
stability.

\item Experiments obtained with our synthesiser show that the combination 
of interval arithmetic to represent the controller coefficients and a two-stage 
verification approach to continuously refine precision, we are able to compute 
a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
given a set of continuous and discrete plant with parametric uncertainties.

@@

\begin{myassumption}
\label{whitenoise}
%
The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are bounded uncorrelated white noises.
% 
\end{myassumption}

@@

Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
assuming a precision \param{I_b}{F_b} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

@@

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with an algorithm for verifying robust closed-loop stability, 
in order to compute a parametric solution for a digital controller given 
a continuous (or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems.  We will also consider performance requirements while
synthesising the digital controller.
